---
title: "MT5125 - Data Analytics - Workshop 2 - Part 3"
subtitle: "Practice Writting Research Reports"
author: "Damien Dupré"
date: "Dublin City University"
output:
  xaringan::moon_reader:
    css: ["default", "metropolis", "metropolis-fonts", "css/custom_design.css"]
    lib_dir: libs
    nature:
      beforeInit: "libs/cols_macro.js"
      highlightStyle: zenburn
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
# libraries --------------------------------------------------------------------
library(countdown)
library(knitr)
# chunk options ----------------------------------------------------------------
opts_chunk$set(
  echo = FALSE,
  fig.align = "center", 
  fig.retina = 3
  )
```

# Team Challenge!

### .center[You have 30 min to **work as a team to write a research report** using `organisation_alpha.xlsx`]

### .center[Here is your research question: **What is the influence of Salary and Gender on Job Satisfaction?** Make your own hypoteses from it]

### .center[Use a **google doc** for everyone to work on it simultaneously]

### .center[Use at least **3 references** in your literature review]

### .center[Remember, the variables `q1` to `q9` are questions from a **Job Satisfaction survey**]

```{r}
countdown(minutes = 30, warn_when = 300, play_sound = TRUE)
```